---
title: "Weight of Fish"
author: "Emann Malik"
date: "April 22, 2021"
output: 
  html_document:
    number_sections: true
    toc: true
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(car)
```
  
```{r include = FALSE}
allFish <- read.csv(file = "Fish.csv")
allFish$Species <- as.factor(allFish$Species)
levels(allFish$Species)
```
  
# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
  
## Build the best regression model you can that predicts the weight of perch
## Using only two predictor variables  
  
# Perch
  
```{r include = FALSE}
Perch <- subset(allFish, Species == "Perch")
Perch <- select(Perch, -Species)
```  
  
## Adjusted R-squared 
  
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
  
The adjusted R-squared plot above shows that the best 2-regressor model of all the other models for Perch is H-W (Height and Width), since it has the highest adjusted R-squared (about 0.94).   
  
## Which is best? 
  
```{r}
which.max(summary.out$adjr2)
```
```{r}
summary.out$which[2,]
```
  
The summary above confirms that the best 2-regressor model is the one that contains height and width.   
  
## Perch model
  
```{r}
perchModel <- lm(Weight ~ Height + Width, data = Perch)
summary.lm(perchModel)
```
  
The summary of the linear model of Height + Width above shows a residual standard error of 85.17 (how far the standard deviation of the model is from that of the normal curve), multiple R-squared of 0.9421 (which means that this model has a strong linear relationship between the two regressors since it is close to 1), and an adjusted R-squared of 0.94 (which is very good since it means that 94% of the mean model error is explained with this model). This model is the best for predicting the weight of Perch because its R-squared is the highest.
  
# Bream
  
# Smelt  
  
  
  