---
title: "Weight of Fish"
author: "Emann Malik"
date: "April 22, 2021"
output: 
  html_document:
    number_sections: true
    toc: true
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(car)
```
  
```{r include = FALSE}
allFish <- read.csv(file = "Fish.csv")
allFish$Species <- as.factor(allFish$Species)
levels(allFish$Species)
```
  
# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
  
In this report, we will show the best 2-regressor model for predicting the weight of Perch, the best 2-regressor model for predicting the weight of Bream, and the best 2-regressor model for predicting the weight of Smelt. The data to be used comes from the "Fish.csv" data set, with focus on the species Perch, Bream, and Smelt. We will be attempting to answer this research question: What is the best 2-regressor model for predicting the weight of Perch, Bream, and Smelt, respectively?
  
## Build the best regression model you can that predicts the weight of perch
## Using only two predictor variables  
  
# Perch
  
```{r include = FALSE}
Perch <- subset(allFish, Species == "Perch")
Perch <- select(Perch, -Species)
```  
  
## Adjusted R-squared 
  
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
  
The adjusted R-squared plot above shows that the best 2-regressor model for predicting the weight of Perch is H-W (Height and Width), since it has the highest adjusted R-squared of any other 2-regressor model (0.94).   
  
## Which is best? 
  
```{r}
which.max(summary.out$adjr2)
```
```{r}
summary.out$which[2,]
```
  
The summary above confirms that the best 2-regressor model is the one that contains Height and Width.   
  
## Perch model
  
```{r}
perchModel <- lm(Weight ~ Height + Width, data = Perch)
summary.lm(perchModel)
```
  
The numerical summary of the linear model of Height + Width above shows a residual standard error of 85.17 (how far the standard deviation of the model is from that of the normal curve), multiple R-squared of 0.9421 (which means that this model has a strong linear relationship since this number is close to 1), and adjusted R-squared of 0.94 (which is very good since it means that 94% of the mean model error is explained with this model). H-W is the best 2-regressor model for predicting the weight of Perch because its adjusted R-squared is the highest.
  
# Bream
  
```{r include = FALSE}
Bream <- subset(allFish, Species == "Bream")
Bream <- select(Bream, -Species)
```   
  
## Adjusted R-squared 
  
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Bream,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```  
  
The adjusted R-squared plot above shows that the best 2-regressor model for predicting the weight of Bream is L2-H (Length2 and Height), since it has the highest adjusted R-squared of any other 2-regressor model (0.9356).  
  
## Which is best? 
  
```{r}
which.max(summary.out$adjr2)
```  
  
```{r}
summary.out$which[3,]
```  
  
The summary above shows that the best model of all for predicting the weight of Bream is L1-H-W (Length1, Height, and Width). Yet, within the context of this report, we are only interested in the best 2-regressor model for this prediction, so L2-H (Length2 and Height) is therefore the best one. 
  
## Bream model
  
```{r}
breamModel <- lm(Weight ~ Length2 + Height, data = Bream)
summary.lm(breamModel)
```  
  
The numerical summary of the linear model of Length2 + Height above shows a residual standard error of 53.1 (how far the standard deviation of the model is from that of the normal curve), multiple R-squared of 0.9394 (which means that this model has a strong linear relationship since this number is close to 1), and adjusted R-squared of 0.9356 (which is very good since it means that about 94% of the mean model error is explained with this model). This is the best 2-regressor model for predicting the weight of Bream because its adjusted R-squared is the highest.  
  
# Smelt  
  
```{r include = FALSE}
Smelt <- subset(allFish, Species == "Smelt")
Smelt <- select(Smelt, -Species)
```  
  
## Adjusted R-squared 
  
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Smelt,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```  
  
The adjusted R-squared plot above shows that the best 2-regressor model for predicting the weight of Smelt is L2-W (Length2 and Width), since it has the highest adjusted R-squared of any other 2-regressor model (0.9645).
  
## Which is best? 
  
```{r}
which.max(summary.out$adjr2)
```  
  
```{r}
summary.out$which[4,]
```    
  
The summary above shows that the best model of all for predicting the weight of Smelt is L1-L2-H-W (Length1, Length2, Height, and Width). Yet, within the context of this report, we are only interested in the best 2-regressor model for this prediction, so L2-W (Length2 and Width) is therefore the best one.  
  
## Smelt model
  
```{r}
smeltModel <- lm(Weight ~ Length2 + Width, data = Smelt)
summary.lm(smeltModel)
```   
  
The numerical summary of the linear model of Length2 + Width above shows a residual standard error of 0.7783 (how far the standard deviation of the model is from that of the normal curve), multiple R-squared of 0.97 (which means that this model has a strong linear relationship since this number is close to 1), and adjusted R-squared of 0.9645 (which is very good since it means that about 96% of the mean model error is explained with this model). This is the best 2-regressor model for predicting the weight of Smelt because its adjusted R-squared is the highest.  
  
# Conclusion  
  
In conclusion, we have found that the best 2-regressor model for predicting the weight of Perch is H-W (Height and Width), the best 2-regressor model for predicting the weight of Bream is L2-H (Length2 and Height), and the best 2-regressor model for predicting the weight of Smelt is L2-W (Length2 and Width).
  